Paper Figures

### 2019-09-12 PaperFigures.Rmd
added in space for flow plots and letters for labeling

---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "8/27/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

@@

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), axis.text.x = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    theme(text = element_text(size=20))+
    theme(plot.subtitle = element_text(hjust = 0.5))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10)+
    labs(x="", y="")
}

@@

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-read.csv("OG_CD4_bulk_summary_clean.csv")
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

cowplot::plot_grid(tf, sm)

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups, ncol=2)+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = cyt_groups, ncol=2)+
    coord_cartesian(ylim=c(0,8))

cowplot::plot_grid(one, two)
```

```{r pvals for ifng and tnfa}
y<-split(cyt,cyt$SM) 
A<-lapply(y, function(g) kruskal.test(IFNg~TB, g))
B<-lapply(y, function(g) kruskal.test(TNFa~TB, g))

pval<-c(A$`SM-`$p.value, A$`SM+`$p.value, B$`SM-`$p.value, B$`SM+`$p.value)
comparison<-c("SM- IFNγ", "SM+ IFNγ", "SM- TNFα", "SM+ TNFα")
kable(cbind(comparison, pval))
```

####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=8}
melt<-melt(subset(CYT, CYT$Stim=="PMA"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) CD4+ T cells")+coord_cartesian(ylim=c(0,45))

cyt<-filter_ltbi(melt)
b<-baseplot(cyt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))

cyt<-filter_tb(melt)
c<-baseplot(cyt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))

cowplot::plot_grid(a, b, c, ncol=3)
```

####Generic TH1 and TH2 cytokine producing cells are stratified by lineage-specific transcription factors, and CCR4
Amongst TH1 cytokine producing CD4+ T cells, moderate frequencies express the transcription factor T-bet while very low frequencies express GATA3. In contrast, amongst TH2 cytokine producing CD4+ T cells, low frequencies express T-bet while high frequencies express GATA3. Similarly high frequencies of TH2 cytokine producing cells express CCR4 compared to TH1 cytokine producing cells. Both TH1 and TH2 cells have equivalent moderate frequencies of CXCR3 expressing cells. There are no differences by S. mansoni status.

@@

a<-booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells")

@@

b<-booleanplot(test, "SM","value", ltbi.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))

@@

c<-booleanplot(test, "SM","value", tb.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))

cowplot::plot_grid(a, b, c, ncol=3)
```

#LTBI

####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific cytokine production, specifically due to higher production of IFNγ
```{r, narrow down ltbi data}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))
```

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

cowplot::plot_grid(a, b)
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

cowplot::plot_grid(a,b,ncol=2)
```

#TB 
```{r, narrow down tb data}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))
```

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))

cowplot::plot_grid(a, b)
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

cowplot::plot_grid(a, b, ncol=2)
```

```{r receptor on gata3, fig.width=7.5, fig.height=8}
phen$TH1_GATA4notCCR4<-rowSums(phen[,grep("TH1_._g_._x", names(phen))])
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_GATA3CCR4", "TH1_GATA4notCCR4"))

@@

baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")
```

#Proliferation Assay
##All Groups Responses to SEB
```{r}
og<-plot_filter(subset(OG, OG$Stim=="SEB"))
ogphen<-plot_filter(subset(OGPHEN, OGPHEN$Stim=="SEB"))
```

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG_freq" = "Proliferation","IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG_freq")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq"))

@@

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4_freq"))

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)

cowplot::plot_grid(og, one, two, ncol=3, rel_widths = c(1.2,2,1))
```

@@

cowplot::plot_grid(tf, sm)
```

##Mtb-Specific Responses in LTBI
```{r}
og<-filter_ltbi(subset(OG, OG$Stim=="PEP"))
ogphen<-filter_ltbi(subset(OGPHEN, OGPHEN$Stim=="PEP"))
oggt<-filter_ltbi(subset(OG.GT, OG.GT$Stim=="PEP"))
ogth1<-filter_ltbi(subset(OG.th1, OG.GT$Stim=="PEP"))
```

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG_freq" = "Proliferation","IFNg_freq" = "IFNγ", 
                    "TNFa_freq" = "TNFα", "IL4_freq" = "IL-4"))

melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG_freq")
og<-baseplot(melt, "TB", "value", ltbi.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    coord_cartesian(ylim=c(0,3))+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg_freq", "TNFa_freq"))
one<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4_freq"))
two<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)

cowplot::plot_grid(og, one, two, ncol=3, rel_widths = c(1.2,2,1))
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

b<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

cowplot::plot_grid(a,b,ncol=2)
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

>>>>

---
title: "Paper Figures"
author: "Taryn McLaughlin"
date: "8/28/2019"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, comment=NA, warning=FALSE, echo=FALSE)
library(dplyr)
library(knitr)
library(ggplot2)
library(gridExtra)
library(GGally)
library(ggpubr)
library(cowplot)
library(tidyr)
library(reshape2)
library(cowplot)
library(corrplot)
library(sjPlot)
```

@@

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=16), axis.text.x = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10)+
    labs(x="", y="")
}

@@

```{r load data}
setwd("/Applications/Old Computer/Day Lab/Flow-Data/clean/")
CD4<-read.csv("ICS_CD4_clean.csv")
CYT<-read.csv("ICS_CD4_Cytokine_clean.csv")
PHEN<-read.csv("ICS_CD4_phenotyping_clean_NAs.csv")
OG<-data.table(read.csv("OG_CD4_bulk_summary_clean.csv"))
OGPHEN<-read.csv("OG_CD4_OG_summary_clean_NAs.csv")
OG.IFNg<-read.csv("OG_CD4_OG.IFNg_summary_clean_NAs.csv")
OG.GT<-read.csv("OG_CD4_OG.GT_summary_clean_NAs.csv")
OG.th1<-read.csv("OG_CD4_OG.TH1_summary_clean_NAs.csv")
luminex<-read.csv("/Applications/Old Computer/Day Lab/Luminex/Clean Data/Luminex_combined_background.txt")
```

@@

#Figure 1
```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

@@

sm<-allplot(melt, "TB", "value", all.cols) +    
    labs(y="(%) Total CD4+ T cells")

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

```{r pvals for ifng and tnfa}
kable(table(cd4$disease), caption="Total CD4 Phenotypes")
kable(table(cyt$disease), caption="Total CD4 Cytokine")

y<-split(cyt,cyt$SM) 
A<-lapply(y, function(g) kruskal.test(IFNg~TB, g))
B<-lapply(y, function(g) kruskal.test(TNFa~TB, g))

pval<-c(A$`SM-`$p.value, A$`SM+`$p.value, B$`SM-`$p.value, B$`SM+`$p.value)
comparison<-c("SM- IFNγ", "SM+ IFNγ", "SM- TNFα", "SM+ TNFα")
kable(cbind(comparison, pval), caption="Stats across Tb groups")
```

#Figure 2
####Generic cytokine production from CD4+ T cells stimulated with PMA & Ionomycin does not differ between SM- and SM+ Healthy Adults
```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

one<-allplot(melt, "TB", "value", all.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,8))+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(subset(CYT, CYT$Stim=="PMA"), 
           id.vars=c("TB","SM"), 
           measure.vars=c("TH1.Freq", "TH1.2.Freq", "TH2.Freq"))
th_groups <- as_labeller(c("TH1.Freq" = "TH1", 
                    "TH1.2.Freq" = "TH1/2", "TH2.Freq" = "TH2"))

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,45))+
    labs(title="Healthy Controls")

cyt<-filter_ltbi(melt)
b<-baseplot(cyt, "SM", "value", ltbi.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))+
    labs(title="LTBI")

cyt<-filter_tb(melt)
c<-baseplot(cyt, "SM", "value", tb.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    coord_cartesian(ylim=c(0,45))+
    labs(title="TB")

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(one, two, labels = c('C', 'D'), nrow=1, label_size = 20)
third_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('E'), label_size = 20)
figure2 = cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

#Figure 3
####Generic TH1 and TH2 cytokine producing cells are stratified by lineage-specific transcription factors, and CCR4
Amongst TH1 cytokine producing CD4+ T cells, moderate frequencies express the transcription factor T-bet while very low frequencies express GATA3. In contrast, amongst TH2 cytokine producing CD4+ T cells, low frequencies express T-bet while high frequencies express GATA3. Similarly high frequencies of TH2 cytokine producing cells express CCR4 compared to TH1 cytokine producing cells. Both TH1 and TH2 cells have equivalent moderate frequencies of CXCR3 expressing cells. There are no differences by S. mansoni status.

@@

a<-booleanplot(test, "SM","value", healthy.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="HC")

@@

b<-booleanplot(test, "SM","value", ltbi.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="LTBI")

@@

c<-booleanplot(test, "SM","value", tb.cols)+
    facet_grid(variable~subset, scales="free")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    labs(y="(%) Cytokine+ CD4+ T cells",
         title="TB")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, c, nrow=1, labels=c('B', 'C', 'D'), label_size = 20)
figure3 <- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,4))
```

#LTBI
#Figure 4
####LTBI individuals coinfected with S. mansoni have higher Mtb peptide-specific cytokine production, specifically due to higher production of IFNγ
```{r, narrow down ltbi data}
cyt<-filter_ltbi(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_ltbi(subset(PHEN, PHEN$Stim=="PEP"))

kable(table(cyt$disease), caption="Pep cytokine")
kable(table(phen$disease[!is.na(phen$TH1_MFI_CCR4)]), caption="Pep phenotype")
```

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(a, b, nrow=1, labels=c('B', 'C'), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, nrow=1, labels=c('D', 'E'), label_size = 20)
figure4 <- cowplot::plot_grid(first_row, second_row, third_row, ncol=1, rel_heights = c(1,2,2))
```

#TB 
#Figure 5
```{r, narrow down tb data}
cyt<-filter_tb(subset(CYT, CYT$Stim=="PEP"))
phen<-filter_tb(subset(PHEN, PHEN$Stim=="PEP"))

kable(table(cyt$disease), caption="Pep cytokine")
kable(table(phen$disease[!is.na(phen$TH1_MFI_CCR4)]), caption="Pep phenotype")
```

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

phen$TH1_GATA4notCCR4<-rowSums(phen[,grep("TH1_._g_._x", names(phen))])
melt<-melt(phen, id.vars=c("TB","SM", "disease"), measure.vars=c("TH1_GATA3CCR4", "TH1_GATA4notCCR4"))

@@

both<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

tbcyt<-cowplot::plot_grid(NULL, a, b, nrow=1, labels=c("A","B", "C"), label_size = 20, rel_widths = c(1.5,1,1))
tbphen<-cowplot::plot_grid(tf, sm, both, nrow=1, labels=c("D","E","F"), label_size = 20)
figure5<-cowplot::plot_grid(tbcyt, tbphen, nrow=2, rel_heights = c(2,3))
```

#Proliferation Assay
#Figure 6
##All Groups Responses to SEB
```{r}
og<-plot_filter(dplyr::filter(OG, Stim=="SEB"))
ogphen<-plot_filter(dplyr::filter(OGPHEN, Stim=="SEB"))

kable(table(og$disease), caption="Total Proliferation")
kable(table(ogphen$disease[!is.na(ogphen$IFNg)]), caption="SEB phenotype")
```

```{r, proliferation and total cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))

@@

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)
```

@@

first_row = cowplot::plot_grid(NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c("E", "F"), nrow=1, label_size = 20)
figure6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

#Figure 7
##Mtb-Specific Responses in LTBI
```{r}
og<-filter_ltbi(dplyr::filter(OG, Stim=="PEP"))
ogphen<-filter_ltbi(dplyr::filter(OGPHEN, Stim=="PEP"))
oggt<-filter_ltbi(dplyr::filter(OG.GT, Stim=="PEP"))
ogth1<-filter_ltbi(dplyr::filter(OG.th1, Stim=="PEP"))

kable(table(og$disease), caption="PEP Proliferation")
kable(table(ogphen$disease[!is.na(ogphen$IFNg)]), caption="PEP phenotype")
```

####There are no differences in Mtb-specific proliferation betweeen SM+ and SM- QF+ individuals. The cytokine production from expanded Mtb-specific CD4+ T cells only differs with regards to IFNγ IL-4 co-production, however the frequency of these cells is incredibly low. The dominant cytokine subgroup is still cells that co-produce IFNγ and TNFα. 
```{r og and cyt, fig.width=15, fig.height=8}
groups <- as_labeller(c("OG" = "Proliferation","IFNg" = "IFNγ", 
                    "TNFa" = "TNFα", "IL4" = "IL-4"))

melt<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-baseplot(melt, "TB", "value", ltbi.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    coord_cartesian(ylim=c(0,3))+
    labs(y="(%) Total CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
one<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups, ncol=2)+
    labs(y="(%) Proliferating CD4+ T cells")

melt<-melt(ogphen, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4"))
two<-baseplot(melt, "TB", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = groups)
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c("E", "F"), nrow=1, label_size = 20)
figure7<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

@@

a<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")
